Forecasting the 2024 U.S. Presidential Election

### 2024-11-02 paper/paper.qmd
Revise title, subtitle, abstract, measurement.

---
title: "Predicting Kamala Harris's Victory in the 2024 US Election"
subtitle: "Poll Data Predicts Kamala Harris Win with 387 Electoral Votes"
author: 
  - Xuanle Zhou
  - Yongqi Liu
  - Yuxuan Wei
thanks: "Code and data are available at: https://github.com/wyx827/2024USpresidentialelection.git"
date: today
date-format: long
toc: true
abstract: "This study provides a prediction for the 2024 U.S. presidential election, presenting potential outcomes based on a state-by-state electoral vote analysis. These projections can guide campaign strategies and influence public discourse. The results suggest Kamala Harris will secure a win with 387 electoral votes, significantly surpassing the 270 needed for victory. In contrast, Donald Trump is predicted to receive 151 electoral votes."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

In this analysis, the estimand is the true effect of polling factors on projected support for Trump and Harris in the 2024 U.S. election. Specifically, it reflects how variables such as poll quality, transparency, sample size, and timing influence the predicted vote percentages for Kamala Harris and Donald Trump across states. Defining the estimand clearly ensures consistency in the analysis by guiding model design and interpretation, preventing unintended shifts in focus due to minor methodological changes.

@@

## Data Measurement and Considerations

The dataset used in this analysis originates from @fivethirty, a trusted source known for its rigorous methodology in collecting and aggregating polling data to represent public opinion accurately. To maintain data integrity and ensure a high standard of reliability, only polls meeting stringent quality criteria are included in the dataset. Specifically, each poll must disclose important information, including the pollster’s name, the exact dates of the survey, the sample size, and the full methodological details. These details encompass the polling medium (e.g., phone, online), use of verified voter files, demographic weighting criteria, and any adjustments applied to reflect a representative sample.

Polls are rigorously verified, and those that do not meet these requirements are excluded from the dataset. For instance, polls categorized as nonscientific, those that merge data from multiple unrelated sources, and those conducted by hobbyists or unverified entities are filtered out to prevent data quality compromise.

Once verified as credible, polls are incorporated into the FiveThirtyEight database. These polls then contribute to polling averages, forecast models, and political analysis, all of which rely on high-quality, reliable public opinion data. This careful selection process ensures that the dataset reflects a thorough and detailed view of public sentiment, accurately capturing behavioral trends and preferences over time.

>>>>

---
title: "Forecasting the 2024 U.S. Presidential Election"
subtitle: "Predicting Kamala Harris’s Path to Victory: A Poll-Based Projection Under Electoral Uncertainty"
author: 
  - Xuanle Zhou
  - Yongqi Liu
  - Yuxuan Wei
thanks: "Code and data are available at: https://github.com/wyx827/2024USpresidentialelection.git"
date: today
date-format: long
toc: true
abstract: "This study provides a predictive analysis of the 2024 U.S. presidential election, presenting potential outcomes through a state-by-state evaluation of electoral votes. These projections can guide campaign strategies and influence public discourse. The results suggest Kamala Harris will secure a win with 387 electoral votes, significantly surpassing the 270 needed for victory and indicating a landslide. In contrast, Donald Trump is predicted to receive 151 electoral votes."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

## Estimand
In this analysis, the estimand is the true effect of polling factors on projected support for Trump and Harris in the 2024 U.S. election. Specifically, it reflects how variables such as poll quality, transparency, sample size, and timing influence the predicted vote percentages for Kamala Harris and Donald Trump across states. Defining the estimand clearly ensures consistency in the analysis by guiding model design and interpretation, preventing unintended shifts in focus due to minor methodological changes.

###

@@

## Measurement and Considerations

The goal of measurement here is to translate individual voter opinions into a reliable estimate of electoral college outcomes. This analysis aims to systematically capture public sentiment through polling data and convert it into a structured forecast of electoral support for each candidate.

- Data Source and Quality Assurance: The dataset is sourced from @fivethirty, a trusted platform recognized for its stringent standards in polling data quality. Only polls meeting high-quality criteria are included to ensure broad representation of likely U.S. voters. Each poll provides essential details, including the pollster’s identity, survey dates, sample size, and methodological transparency. These methods include data collection medium (e.g., phone, online), use of voter files, demographic weighting, and adjustments to create a representative sample. While these standards help capture respondents’ voting intentions accurately, it’s important to note that these criteria rely on historical benchmarks, potentially overlooking recent methodological shifts or emerging biases.
- Temporal Limitations and Data Recency: Polling data captures discrete snapshots of voter sentiment rather than continuous updates. Consequently, the analysis reflects voter intentions only at specific moments, which may not capture rapid opinion shifts, particularly as Election Day approaches. To mitigate this limitation, recency adjustments are applied to account for the time elapsed since each poll was conducted, helping to ensure that the data remains reflective of current voter sentiment.
- Participation and Response Bias: Despite the rigorous methodology, certain biases in survey participation are difficult to avoid. Self-selection bias (where individuals choose whether to participate) and social desirability bias (where respondents may adjust their responses to be more socially acceptable) can affect data accuracy. These biases may introduce discrepancies between expressed opinions and actual voting behavior, potentially influencing forecast reliability.
- Regional Sampling Imbalances: The frequency of polling varies significantly by state, with battleground states receiving more frequent attention than states considered “safe.” This uneven distribution can lead to imbalances in regional representation, which might skew state-level and, by extension, national forecasts. Such discrepancies highlight the challenge of producing a uniformly accurate forecast across all regions.
